Approximation as Differentiation

### 2025-04-02 notes/sec/cmon-enriched.tex
Be more explicit about V-enriched functors.

For any monoidal category $V$ and $V$-enriched categories $C$ and $D$, the action of a \emph{$V$-enriched}
functor $F: C \to D$ on morphisms takes the form of a morphism $\Hom{C}{X}{Y} \to \Hom{D}{F(X)}{F(Y)}$ between
hom-monoids in $V$. In the specific setting of a $\CMon$-enriched presheaf $F: C^\op \to \CMon$, this means
that $F$ preserves the additive structure of morphisms:
\begin{itemize}
\item $F(0_{X,Y}) = 0_{F(Y),F(X)}$
\item $F(f + g) = F(f) + F(g)$
\end{itemize}
It then follows automatically that $F$ also preserves bilinear composition, i.e.:
\begin{itemize}
\item $F(f) \comp F(0) = F(f) = F(0) \comp F(f)$
\item $F(f + g) \comp F(h) = F(h \comp f) + F(h \comp g)$
\item $F(h) \comp F(f + g) = F(f \comp h) + F(g \comp h)$
\end{itemize}
in addition to the usual functorial properties.

@@

Suppose $C$ a small category. The standard \emph{Yoneda embedding} for $C$ is the functor $\Yoneda: C \to
\Func{C^\op}{\Set}$ sending:
\begin{itemize}
\item any object $X$ in $C$ to the contravariant hom-functor $\Yoneda(X) = \Hom{C}{-}{X}$ which sends:
\begin{itemize}
\item any object $Y$ in $C$ to the hom-set $\Hom{C}{Y}{X}$;
\item any morphism $f: Y \to Z$ in $C$ to the function $\Hom{C}{f}{X} = (- \comp f): \Hom{C}{Z}{X} \to
\Hom{C}{Y}{X}$.
\end{itemize}
\item any morphism $f: X \to Y$ in $C$ to the natural transformation $\Yoneda(f)$ where $\Yoneda(f)_Z = (f
\comp -): \Hom{C}{Z}{X} \to \Hom{C}{Z}{Y}$.
\end{itemize}

>>>>

For any monoidal category $\mathscr{V}$ and $V$-enriched categories $C$ and $D$, the action of a
\emph{$\mathscr{V}$-enriched} functor $F: C \to D$ on morphisms takes the form of a morphism $F_{X,Y}:
\Hom{C}{X}{Y} \to \Hom{D}{F(X)}{F(Y)}$ between hom-objects in $\mathscr{V}$ that is
\emph{$\mathscr{V}$-natural}, i.e.~makes the following diagram commute:

\begin{center}
\begin{tikzcd}
   \Hom{C}{Y}{Z} \tensor \Hom{C}{X}{Y} \arrow[r, "- \comp -"] \arrow[d, "F_{Y,Z} \tensor F_{X,Y}"'] & \Hom{C}{X}{Z} \arrow[d, "F_{X,Z}"] \\
   \Hom{D}{F(Y)}{F(Z)} \tensor \Hom{D}{F(X)}{F(Y)} \arrow[r, "- \comp -"'] & \Hom{D}{F(X)}{F(Z)}
\end{tikzcd}
\end{center}

Write $\Func{C}{D}_{\mathscr{V}}$ for the category of $\mathscr{V}$-enriched functors from $C$ to $D$. In the
specific setting of a $\CMon$-enriched presheaf $F: C^\op \to \CMon$, this means that $F$ preserves the
additive structure of morphisms:
\begin{itemize}
\item $F(0_{X,Y}) = 0_{F(Y),F(X)}$
\item $F(f + g) = F(f) + F(g)$
\end{itemize}
It then follows automatically that $F$ also preserves bilinear composition, i.e.:
\begin{itemize}
\item $F(f) \comp F(0) = F(f) = F(0) \comp F(f)$
\item $F(f + g) \comp F(h) = F(h \comp f) + F(h \comp g)$
\item $F(h) \comp F(f + g) = F(f \comp h) + F(g \comp h)$
\end{itemize}
in addition to the usual functorial properties.

@@

Suppose $C$ a small category. The usual \emph{Yoneda embedding} for $C$ is the functor $\Yoneda: C \to
\Func{C^\op}{\Set}$ sending:
\begin{itemize}
\item any object $X$ in $C$ to the contravariant hom-functor $\Yoneda(X) = \Hom{C}{-}{X}: C \to \Set$ which
sends:
   \begin{itemize}
   \item any object $Y$ in $C$ to the hom-set $\Hom{C}{Y}{X}$;
   \item any morphism $f: Y \to Z$ in $C$ to the function $\Hom{C}{f}{X} = (- \comp f): \Hom{C}{Z}{X} \to
   \Hom{C}{Y}{X}$.
   \end{itemize}
\item any morphism $f: X \to Y$ in $C$ to the natural transformation $\Yoneda(f)$ where $\Yoneda(f)_Z = (f
\comp -): \Hom{C}{Z}{X} \to \Hom{C}{Z}{Y}$.
\end{itemize}

\noindent For a $\mathscr{V}$-enriched category $C$, the hom-functor $\Hom{C}{-}{X}: C \to \mathscr{V}$ sends
objects $Y$ in $C$ to hom-objects $\Hom{C}{Y}{X}$ in $\mathscr{V}$ and morphisms $f: Y \to Z$ in $C$ to
morphisms

\noindent For $\CMon$-enriched $C$, there is an enriched version of the Yoneda embedding, namely the
$\CMon$-enriched functor $\Yoneda_{\CMon}: C \to \Func{C^\op}{\CMon}_{\CMon}$. First we note that the
hom-functor $\Hom{C}{-}{X}: C \to \CMon$ is $\CMon$-enriched because composition is bilinear and so $(- \comp
f)$ preserves the additive structure of morphisms.
